### 2020-01-31 wuhan.tex
.
push again

We strongly emphasize the value of attention to accurate characterization of the transmission chains via contact tracing and better statistical framework for inferring generation-interval distributions from such data \citep{britton2019estimation}.
A combined effort between public-health workers and modelers in this direction will be crucial for predicting the course of an epidemic and controlling it.
%% \jd{Leave the medical folks out; we don't want to ad

@@

\mli{Nevertheless, this is our best approximation in estimating the potential growth rate, and R0 and its uncertainty from these studies. To confidently evaluate and compare these parameters across studies, we would need to know the assumptions made from each research and be able to reproduce their estimates. Initial estimates of R0 is essential to guide control; however, discrepancies in parameter estimates (and uncertainties) across studies using similar information of the same outbreak can be a potential step back in making control. (i.e., are these ranges in R0 estimates due to assumptions modelers make, or is R0 more uncertain when we think?). To aid policymakers to guide control, we suggest modelers to (1) propagate uncertainties in parameters and honestly report them, (2) reproducible methods. 
}

>>>>

We strongly emphasize the value of attention to accurate characterization of the transmission chains via contact tracing and better statistical framework for inferring generation-interval distributions from such data \citep{britton2019estimation}.
A combined effort between public-health workers and modelers in this direction will be crucial for predicting the course of an epidemic and controlling it.
%% \jd{Leave the medical folks out; we don't want to add to the pressure on them during an outbreak.}
We also emphasize the value of transparency from modelers. 
Model estimates during an outbreak, even in pre-prints, should include code links and complete explanations. 
Ideally, the code should not rely on closed-source programs.

@@

%% \mli{Nevertheless, this is our best approximation in estimating the potential growth rate, and R0 and its uncertainty from these studies. To confidently evaluate and compare these parameters across studies, we would need to know the assumptions made from each research and be able to reproduce their estimates. Initial estimates of R0 is essential to guide control; however, discrepancies in parameter estimates (and uncertainties) across studies using similar information of the same outbreak can be a potential step back in making control. (i.e., are these ranges in R0 estimates due to assumptions modelers make, or is R0 more uncertain when we think?). To aid policymakers to guide control, we suggest modelers to (1) propagate uncertainties in parameters and honestly report them, (2) reproducible methods. 
}
